\documentclass[11pt,a4paper]{article}

% ---------------------------------------------------------------------------
% Software Requirements Specification
% 3D House Defense Game Implemented with WebGL and Three.js
% ---------------------------------------------------------------------------

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{titlesec}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  pdftitle={SRS - 3D House Defense Game},
  pdfauthor={Nguyen Thuy Ngoc}
}

% Code listing style for the GameState example
\definecolor{codebg}{rgb}{0.96,0.96,0.96}
\lstdefinestyle{tslisting}{
  backgroundcolor=\color{codebg},
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  framesep=6pt,
  keywordstyle=\color{blue},
  showstringspaces=false,
  language=Java
}

\setlist{nosep,leftmargin=1.6em}
\renewcommand{\arraystretch}{1.25}

% ---------------------------------------------------------------------------

\begin{document}

% ----------------------------- Title Page ----------------------------------
\begin{titlepage}
  \centering
  \vspace*{2cm}

  {\large UNIVERSITY OF SCIENCE AND TECHNOLOGY OF HANOI\par}
  \vspace{2.5cm}

  {\Huge\bfseries Software Requirements Specification\par}
  \vspace{1.5cm}

  {\LARGE 3D House Defense Game Implemented with WebGL and Three.js\par}
  \vspace{3cm}

  \begin{tabular}{ll}
    \textbf{Student:}        & Nguyen Thuy Ngoc \\
    \textbf{Student ID:}     & 23BI14344 \\
    \textbf{Academic Year:}  & 2025--2026 \\
  \end{tabular}

  \vfill
  {\large 2026-06-17\par}
\end{titlepage}

\tableofcontents
\newpage

% ===========================================================================
\section{Introduction}

\subsection{Purpose}

The purpose of this Software Requirements Specification (SRS) is to define the
functional and non-functional requirements of the \emph{3D House Defense Game
Implemented with WebGL and Three.js}. This document serves as a reference for
the analysis, design, implementation, testing, and evaluation of the system
throughout the project lifecycle.

Although the application is presented as a simple 3D defense game, its primary
objective is to demonstrate the development of a modern interactive web
application using frontend technologies. The system is developed with Next.js,
React, TypeScript, and Three.js, providing an opportunity to explore
component-based architecture, type-safe development practices, real-time
rendering, and interactive user experiences within a browser environment.

\subsection{Scope}

The project consists of a browser-based interactive 3D application developed
using modern web technologies. The application is implemented using Next.js as
the frontend framework and TypeScript as the primary programming language.
Three.js and WebGL are used to construct and render the interactive 3D
environment directly within the browser. The application presents a defensive
gameplay scenario in which the player protects a house from approaching
monsters by aiming and firing projectiles.

The game environment includes a house, surrounding yard, fence, monsters, and
weapons rendered within a three-dimensional scene. Players interact with the
application through mouse-based controls to observe the environment, target
enemies, and perform shooting actions.

While the game scenario provides the functional context of the application, the
primary focus of the project is the implementation of frontend systems that
support real-time interaction and rendering. The project demonstrates how
modern web technologies can be used to build responsive and visually rich
browser applications without requiring dedicated game engines or native
software installation.

\subsection{Objectives}

The main objectives of this project are as follows:

\begin{itemize}
  \item Develop a browser-based interactive 3D application using modern
        frontend development practices like Next.js, React, and TypeScript.
  \item Demonstrate the integration of real-time rendering and user interaction
        within a web environment.
  \item Apply fundamental computer graphics concepts such as scene
        construction, lighting, texture mapping, animation, and object
        interaction.
  \item Design and implement gameplay mechanics that provide meaningful
        interaction with the virtual environment.
  \item Explore frontend architectural approaches for managing application
        state and real-time events.
  \item Deliver a complete and functional software product that can be executed
        directly within modern web browsers.
\end{itemize}

\subsection{Document Structure}

This document is organized into five sections.

Section 1 introduces the purpose, scope, objectives, and terminology used
throughout the document.

Section 2 provides an overview of the system, including its background, users,
constraints, and major functionalities.

Section 3 specifies the detailed functional requirements of the application.

Section 4 describes the non-functional requirements that define the quality
attributes of the system.

Section 5 presents potential future enhancements that may be implemented if
additional development time is available.

% ===========================================================================
\section{Overall Description}

\subsection{Project Background}

Recent advances in browser technologies have significantly expanded the
capabilities of frontend web applications. Modern frameworks and graphics
libraries enable developers to build highly interactive experiences that extend
beyond traditional user interfaces and static web pages.

Modern technologies allow developers to create real-time 3D environments
directly within web browsers, making it possible to deliver immersive visual
experiences without requiring native software installation. As a result,
frontend development increasingly involves not only interface construction but
also rendering systems, animation pipelines, user interaction processing, and
performance optimization.

This project explores the intersection between frontend engineering and
computer graphics by developing an interactive 3D application that combines
these technologies within a practical use case.

\subsection{Problem Statement}

Traditional frontend projects often focus on forms, dashboards, and data-driven
interfaces. While these applications demonstrate common web development skills,
they provide limited opportunities to explore advanced interaction models and
real-time rendering techniques.

The challenge addressed by this project is to design and implement a
browser-based application that demonstrates how modern frontend technologies can
support complex interactive experiences. The system must process user input in
real time, manage dynamic objects within a three-dimensional environment,
provide responsive visual feedback, and maintain acceptable rendering
performance throughout gameplay.

\subsection{Game Story}

The player begins by accessing the web application and is presented with a
Welcome Screen. This screen provides a brief introduction to the game and its
objective, along with a button that allows the player to start a new game
session.

After selecting the Start Game button, the player enters the gameplay scene. The
game environment, wave information, gameplay timer, and control panel are
displayed. Before gameplay begins, a countdown sequence consisting of ``3'',
``2'', ``1'', and ``Ready'' is shown on the screen. Three seconds after the
Ready message disappears, the first enemy is spawned.

The player's objective is to defend a house located at the center of the
battlefield. Enemies continuously advance toward the house using non-linear
movement patterns with random directional variations. To encourage distributed
enemy movement and prevent clustering, the front side of the house spans the
entire width of the battlefield.

The game features three enemy types with different health and movement
characteristics. Easy enemies have 100 health points and move at the highest
speed, reaching the house in approximately twenty seconds if not eliminated.
Medium enemies have 200 health points and require approximately twenty-five
seconds to reach the house. Hard enemies have 400 health points and move at the
slowest speed, requiring approximately thirty seconds to reach the house.

To defend the house, the player controls a cannon that fires projectiles toward
selected locations on the battlefield. When the player clicks on the ground, a
visual marker represented by an ``X'' appears at the selected location. The
cannon immediately fires a projectile toward that position. Projectiles travel
using a ballistic trajectory and land after a weapon-dependent travel time.

Three weapon levels are available throughout the game. The player starts with
the Basic Weapon, which deals 30 damage per normal shot and generates a stronger
Big Shot after every three attacks. More powerful weapons are unlocked through
wave progression, providing increased damage output, faster projectile travel
times, and enhanced special attacks.

Damage is calculated when a projectile reaches its landing position. Enemies
located closer to the impact point receive more damage, while enemies farther
away receive less damage. An enemy positioned exactly at the impact location
receives the full damage value of the projectile.

The game is divided into three progressively more difficult waves. Each wave
introduces a predefined combination of enemy types. After all enemies in the
current wave have been defeated, a transition message displaying the upcoming
wave number appears for three seconds before the next wave begins.

The player loses immediately if any enemy successfully crosses the defensive
boundary and reaches the protected area. When this occurs, a defeat overlay is
displayed along with an option to restart the game.

The player wins by successfully completing all three waves and eliminating every
enemy. Upon victory, a congratulatory overlay is displayed together with an
option to return to the Welcome Screen and start a new session.

\subsection{Target Users}

The primary users of the system include students, educators, and individuals
interested in web development, computer graphics, and interactive application
design.

The application is designed for users who have access to a modern desktop web
browser and are capable of interacting with mouse-based controls.

\subsection{System Overview}

The system is a browser-based interactive 3D application in which the player
must defend a house against incoming monsters.

When the application starts, the player is presented with a complete 3D
environment containing a house, yard, fence, monsters, and available weapons.
During gameplay, monsters move toward the protected area while the player uses
mouse controls to aim and shoot projectiles.

The game is organized into three consecutive waves of increasing difficulty. The
player begins with a basic weapon and unlocks additional weapons after
completing each wave. Victory is achieved by eliminating all monsters in the
final wave, while defeat occurs if any monster reaches the house.

From a technical perspective, the application integrates multiple frontend
subsystems including scene rendering, input handling, animation control, object
management, collision processing, state management, and visual feedback
generation.

\subsection{System Context}

The application operates within a web browser for all gameplay and does not
require external services to play.

User interactions are processed locally and rendered in real time through WebGL
using the Three.js framework. All game logic, rendering operations, animation
updates, and interaction handling are executed on the client side.

Persistent player rankings are handled by a lightweight server-side leaderboard
service built with Next.js Route Handlers and a local SQLite database. The
client communicates with this service through a small HTTP API. Aside from this
leaderboard service, the system does not depend on external authentication
services or multiplayer infrastructure.

\subsection{Assumptions and Constraints}

The following assumptions and constraints apply to the project:

\begin{itemize}
  \item Users access the application through a modern browser with WebGL support.
  \item The application is primarily designed for desktop environments.
  \item Mouse input is available for aiming and interaction.
  \item The system is developed as a standalone single-player experience.
  \item Internet connectivity is only required to access the application.
\end{itemize}

\subsection{Product Perspective}

The system is developed as an independent web application intended to
demonstrate the capabilities of modern frontend technologies in creating
interactive real-time experiences.

Rather than focusing on large-scale game development, the project uses a game
scenario as a practical framework for exploring frontend architecture, user
interaction design, 3D rendering techniques, and real-time state management
within browser environments.

The application serves both as a functional product and as a technical
demonstration of frontend engineering concepts applied to computer graphics.

\subsection{Product Functions}

The system provides the following major functions:

\begin{itemize}
  \item Render and manage a complete 3D environment.
  \item Display and control multiple waves of monsters.
  \item Allow players to observe, aim, and interact with the scene.
  \item Support projectile-based shooting mechanics.
  \item Detect collisions between projectiles and monsters.
  \item Manage weapon progression and unlocking mechanisms.
  \item Control game progression, victory conditions, and defeat conditions.
  \item Provide visual feedback through lighting, animation, and interactive
        effects.
  \item Record completed runs and present a ranked player leaderboard.
\end{itemize}

% ===========================================================================
\section{System Architecture}

\subsection{Technology Stack}

The application is developed using modern frontend technologies that support
interactive 3D rendering, real-time user interaction, and maintainable software
architecture.

\begin{center}
\begin{tabular}{ll}
  \toprule
  \textbf{Technology} & \textbf{Purpose} \\
  \midrule
  Next.js        & Application framework and routing system \\
  React          & Component-based user interface architecture \\
  TypeScript     & Static type checking and maintainability \\
  Three.js       & 3D rendering engine \\
  WebGL          & Browser graphics rendering API \\
  Tailwind CSS   & User interface styling \\
  GLTF / GLB     & 3D model format \\
  Route Handlers & Backend HTTP API for the leaderboard (Next.js) \\
  SQLite         & Server-side leaderboard storage \\
  Git            & Version control system \\
  \bottomrule
\end{tabular}
\end{center}

The selected technology stack enables the development of a browser-based 3D
interactive application while maintaining scalability, modularity, and code
quality.

\subsection{Architecture Overview}

The application follows a layered architecture that separates user interface
concerns, state management, gameplay logic, and rendering responsibilities. This
separation improves maintainability, scalability, and extensibility.

\begin{center}
\textbf{UI Layer} $\;\downarrow\;$
\textbf{State Management Layer} $\;\downarrow\;$
\textbf{Systems Layer} $\;\downarrow\;$
\textbf{Rendering Layer}
\end{center}

\subsubsection{UI Layer}
The UI Layer contains React components responsible for presenting information and
receiving user input. Examples include the game canvas, heads-up display,
control panel, and overlay screens.

\subsubsection{State Management Layer}
The State Management Layer serves as the single source of truth for the
application. It stores gameplay data including player information, enemy
entities, projectiles, scores, wave progression, and game settings.

\subsubsection{Systems Layer}
The Systems Layer implements gameplay mechanics through specialized modules such
as movement, collision detection, enemy spawning, shooting logic, and wave
management.

\subsubsection{Rendering Layer}
The Rendering Layer manages the Three.js scene, camera configuration, lighting
setup, model loading, animation updates, and frame rendering.

\subsection{Game Loop Design}

The application operates through a continuous game loop that processes user
input, updates application state, executes gameplay systems, and renders the
scene.

\begin{center}
\textbf{Input} $\;\downarrow\;$
\textbf{Dispatch Action} $\;\downarrow\;$
\textbf{Reducer} $\;\downarrow\;$
\textbf{Update State} $\;\downarrow\;$
\textbf{Run Systems} $\;\downarrow\;$
\textbf{Render Scene}
\end{center}

User actions are converted into application events. These events are processed by
reducers, resulting in state updates. Gameplay systems then execute based on the
latest state before the rendering layer updates the visual scene.

\subsection{State Architecture}

The application utilizes centralized state management to ensure predictable
behavior and consistent synchronization between gameplay systems and user
interface components.

Example structure:

\begin{lstlisting}[style=tslisting]
type GameState = {
  status: "idle" | "playing" | "win" | "lose"

  player: {
    hp: number
  }

  playerName: string | null

  enemies: Enemy[]
  bullets: Bullet[]

  score: number
  wave: number

  settings: {
    enemySpeed: number
    spawnRate: number
  }
}
\end{lstlisting}

The centralized state architecture simplifies data flow and provides a
consistent mechanism for updating gameplay information across the application.

\subsection{UI Flow Document}

\subsubsection{Main User Flow}
The primary interaction flow experienced by the user is illustrated below.

\begin{center}
\textbf{Start Page} $\;\downarrow\;$
\textbf{Start Game} $\;\downarrow\;$
\textbf{Gameplay Loop} $\;\downarrow\;$
\textbf{Wave Progression} $\;\downarrow\;$
\textbf{Win / Lose Screen} $\;\downarrow\;$
\textbf{Restart}
\end{center}

Users begin on the landing page, enter the gameplay environment, progress
through multiple waves, receive a final outcome, and may restart the game.

\subsubsection{Gameplay Flow}
The core gameplay interaction cycle is illustrated below.

\begin{center}
\textbf{Mouse Input} $\;\downarrow\;$
\textbf{Shoot Action} $\;\downarrow\;$
\textbf{Bullet Spawn} $\;\downarrow\;$
\textbf{Collision Detection} $\;\downarrow\;$
\textbf{Enemy Destroyed} $\;\downarrow\;$
\textbf{Score Update}
\end{center}

Players interact with the environment using mouse controls. Successful shooting
actions generate projectiles that may destroy enemies and increase the player's
score.

\subsubsection{Runtime Control Flow}
Runtime settings can dynamically affect gameplay without restarting the
application.

\begin{center}
\textbf{User Changes Settings} $\;\downarrow\;$
\textbf{Dispatch Action} $\;\downarrow\;$
\textbf{Update GameState} $\;\downarrow\;$
\textbf{Systems Read New Values} $\;\downarrow\;$
\textbf{Gameplay Changes Immediately}
\end{center}

This mechanism allows gameplay parameters to be adjusted while the game remains
active.

\subsection{State Diagram Document}

\subsubsection{Game State Transition}

\begin{center}
\begin{tabular}{lll}
  \toprule
  \textbf{Current State} & \textbf{Event} & \textbf{Next State} \\
  \midrule
  Idle    & Start Game        & Playing \\
  Playing & Victory Condition & Win \\
  Playing & Defeat Condition  & Lose \\
  Win     & Restart           & Playing \\
  Lose    & Restart           & Playing \\
  \bottomrule
\end{tabular}
\captionof{table}{Game State Transitions}
\end{center}

The application starts in the idle state and transitions to gameplay when the
user initiates a session. The session concludes with either a victory or defeat
outcome.

\subsubsection{Enemy State}

\begin{center}
\begin{tabular}{ll}
  \toprule
  \textbf{State} & \textbf{Description} \\
  \midrule
  Spawn     & Enemy appears in the game world \\
  Move      & Enemy advances toward the target \\
  Hit       & Enemy receives damage \\
  Destroyed & Enemy is removed from the scene \\
  \bottomrule
\end{tabular}
\end{center}

Each enemy follows a predefined lifecycle from creation to removal.

\subsubsection{Bullet State}

\begin{center}
\begin{tabular}{ll}
  \toprule
  \textbf{State} & \textbf{Description} \\
  \midrule
  Spawn     & Projectile is created \\
  Move      & Projectile travels through the scene \\
  Collision & Projectile hits an enemy \\
  Remove    & Projectile is removed from memory \\
  \bottomrule
\end{tabular}
\end{center}

Bullets are created by shooting actions and remain active until a collision
occurs or cleanup conditions are met.

% ===========================================================================
\section{Functional Requirements}

\subsection{Game Session Management}

This subsystem controls the complete lifecycle of a gameplay session, from the
moment a user accesses the website until active gameplay begins.

The subsystem is responsible for displaying the welcome page, creating a new game
session, initializing all gameplay data, presenting the countdown sequence, and
activating enemy spawning.

\subsubsection{FR-1 Welcome Screen}

\paragraph{Purpose}
Provide an entry point to the application and explain the objective of the game
before gameplay begins.

\paragraph{Preconditions}
\begin{itemize}
  \item The user accesses the website.
  \item The application has loaded successfully.
\end{itemize}

\paragraph{Main Flow}
\begin{enumerate}
  \item The system displays the Welcome Screen.
  \item The system displays the game title.
  \item The system displays a short description explaining that the player must
        defend a house against incoming monsters.
  \item The system displays a name input field for the leaderboard.
  \item The system displays a ``Play with Name'' button, a ``Pass'' button (play
        anonymously), and a ``View Leaderboard'' option.
  \item The system waits for user interaction.
  \item The user enters a name and clicks ``Play with Name'', or clicks ``Pass''
        to play anonymously.
  \item The system transitions to the Gameplay Scene, carrying the chosen name
        (or none for an anonymous session).
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-1: No gameplay logic shall execute while the Welcome Screen is active.
  \item BR-2: No enemies shall spawn while the Welcome Screen is active.
  \item BR-3: The Start Game controls shall always be visible.
  \item BR-3a: ``Play with Name'' shall be enabled only when a non-empty name is
        entered; ``Pass'' shall always be available.
  \item BR-3b: The Welcome Screen shall allow the player to view the leaderboard
        before starting a session.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item The Welcome Screen is displayed immediately after accessing the website.
  \item The Start Game button is visible and clickable.
  \item Clicking Start Game transitions to the Gameplay Scene.
\end{itemize}

\subsubsection{FR-2 Game Initialization}

\paragraph{Purpose}
Prepare all gameplay resources and application state before gameplay begins.

\paragraph{Trigger}
The user clicks the Start Game button.

\paragraph{Main Flow}
\begin{enumerate}
  \item The system creates a new game session.
  \item The system initializes the game state.
  \item The system loads all required 3D assets.
  \item The system creates the gameplay scene.
  \item The system creates the player entity.
  \item The system creates the house entity.
  \item The system initializes weapon progression.
  \item The system initializes wave progression.
  \item The system initializes the gameplay timer.
  \item The system initializes enemy spawn managers.
  \item The system displays the gameplay interface.
\end{enumerate}

\paragraph{Data Initialization}
The initial state shall be:
\begin{verbatim}
GameStatus  = Countdown
CurrentWave = 1
CurrentWeapon = Basic
Score       = 0
EnemyCount  = 0
ElapsedTime = 0
Countdown   = 3
\end{verbatim}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-4: Previous game data shall not persist.
  \item BR-5: All enemies from previous sessions shall be removed.
  \item BR-6: The player always starts with the Basic weapon.
  \item BR-7: The game always starts at Wave 1.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item All game values are reset.
  \item Wave progression starts from Wave 1.
  \item The Basic weapon is equipped.
\end{itemize}

\subsubsection{FR-3 Countdown Sequence}

\paragraph{Purpose}
Provide a short preparation period before enemy spawning begins.

\paragraph{Main Flow}
\begin{enumerate}
  \item The system displays ``3''.
  \item After 1 second, the system displays ``2''.
  \item After 1 second, the system displays ``1''.
  \item After 1 second, the system displays ``Ready''.
  \item After 1 second, the Ready message disappears.
  \item The system waits 3 additional seconds.
  \item The first enemy is spawned.
  \item The game state changes from Countdown to Playing.
\end{enumerate}

\paragraph{Timing Rules}
\begin{itemize}
  \item TR-1: Each countdown value shall remain visible for exactly 1 second.
  \item TR-2: Enemy spawning is disabled during the countdown.
  \item TR-3: Enemy spawning is disabled while the Ready message is visible.
  \item TR-4: The first enemy shall appear exactly 3 seconds after the Ready
        message disappears.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Countdown values appear in the correct order.
  \item Enemies do not appear before the countdown finishes.
  \item The first enemy appears after the required delay.
\end{itemize}

\subsection{Gameplay Environment}

The Gameplay Environment subsystem defines the virtual battlefield where all
gameplay interactions occur. It is responsible for creating the playable area,
positioning the protected house, defining enemy movement boundaries, and
providing valid target locations for player attacks.

The environment remains active throughout the entire gameplay session and serves
as the reference space for all entities including enemies, projectiles, weapons,
and user interactions.

\subsubsection{FR-5 Battlefield Initialization}

\paragraph{Purpose}
Create the playable area used during gameplay.

\paragraph{Main Flow}
\begin{enumerate}
  \item The system creates the battlefield.
  \item The system loads environmental models.
  \item The system loads the house model.
  \item The system loads fence models.
  \item The system positions all environment objects.
  \item The system enables gameplay interactions.
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-8: The battlefield shall remain visible throughout gameplay.
  \item BR-9: Environmental objects shall not be removed during a session.
  \item BR-10: The house shall always remain at the center of the battlefield.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item The battlefield loads successfully.
  \item The house is visible.
  \item The fence is visible.
\end{itemize}

\subsubsection{FR-6 House Placement}

\paragraph{Purpose}
Define the protected target that players must defend.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-11: The house shall be positioned at the center of the battlefield.
  \item BR-12: The front side of the house shall span the width of the playable
        area.
  \item BR-13: The house shall act as the final objective for enemy movement.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item All enemies move toward the house.
  \item The house remains visible throughout gameplay.
\end{itemize}

\subsubsection{FR-7 Target Area Interaction}

\paragraph{Purpose}
Provide valid locations where players can aim and attack.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-14: Players may only target positions located inside the battlefield.
  \item BR-15: Mouse clicks outside the battlefield shall be ignored.
  \item BR-16: Every valid click shall generate a target position.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Valid clicks generate target positions.
  \item Invalid clicks do not trigger attacks.
\end{itemize}

\subsection{Enemy System}

The Enemy System manages enemy creation, movement, health, damage reception, and
destruction.

Three enemy classes are supported.

\subsubsection{FR-8 Enemy Types}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-17: The Easy enemy shall have 100 HP.
  \item BR-18: The Easy enemy shall reach the house in approximately 20 seconds
        if uninterrupted.
  \item BR-19: The Medium enemy shall have 200 HP.
  \item BR-20: The Medium enemy shall reach the house in approximately 25 seconds
        if uninterrupted.
  \item BR-21: The Hard enemy shall have 400 HP.
  \item BR-22: The Hard enemy shall reach the house in approximately 30 seconds
        if uninterrupted.
\end{itemize}

\subsubsection{FR-9 Enemy Spawn}

\paragraph{Purpose}
Create enemies during active gameplay.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-23: The first enemy shall appear 3 seconds after the Ready message
        disappears.
  \item BR-24: Enemies shall spawn outside the protected area.
  \item BR-25: Spawned enemies shall immediately enter the Move state.
\end{itemize}

\subsubsection{FR-10 Enemy Movement}

\paragraph{Purpose}
Move enemies toward the house.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-26: Enemies shall continuously move toward the house.
  \item BR-27: Enemy movement shall not follow a perfectly straight path.
  \item BR-28: Small random directional offsets shall be applied during movement.
  \item BR-29: Enemy movement shall appear natural and distributed across the
        battlefield.
  \item BR-30: Enemies shall not intentionally cluster into a single point.
\end{itemize}

\subsubsection{FR-11 Enemy Health}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-31: Enemies shall lose health when receiving damage.
  \item BR-32: Enemy health shall never exceed the maximum value assigned to its
        type.
  \item BR-33: An enemy shall be destroyed when health reaches zero.
\end{itemize}

\subsection{Weapon System}

The Weapon System controls weapon progression and damage capabilities.

\subsubsection{FR-12 Basic Weapon}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-34: The Basic weapon shall be the starting weapon.
  \item BR-35: Normal attacks shall deal 80 damage.
  \item BR-36: Every third normal attack shall generate one Big Shot.
  \item BR-37: The Big Shot shall deal 100 damage.
  \item BR-38: The Basic weapon shall have the slowest projectile travel time.
  \item BR-130: The Basic weapon shall require 2 seconds to reload before it can
        fire again.
\end{itemize}

\subsubsection{FR-13 Medium Weapon}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-39: The Medium weapon shall be unlocked after completing Wave 1.
  \item BR-40: Normal attacks shall deal 100 damage.
  \item BR-41: Every fourth normal attack shall generate one Big Shot.
  \item BR-42: The Big Shot shall deal 120 damage.
  \item BR-43: Projectile travel speed shall be faster than the Basic weapon.
  \item BR-131: The Medium weapon shall require 2 seconds to reload before it can
        fire again.
\end{itemize}

\subsubsection{FR-14 Advanced Weapon}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-44: The Advanced weapon shall be unlocked after completing Wave 2.
  \item BR-45: Each attack shall fire two projectiles.
  \item BR-46: Each projectile shall deal 150 damage.
  \item BR-47: Every fifth normal attack shall generate one Big Shot.
  \item BR-48: The Big Shot shall deal 170 damage.
  \item BR-49: Projectile travel speed shall be the fastest among all weapons.
  \item BR-132: The Advanced weapon shall require 3 seconds to reload before it
        can fire again.
\end{itemize}

\paragraph{Weapon Reload Times}
\begin{center}
\begin{tabular}{lc}
  \toprule
  \textbf{Weapon} & \textbf{Reload Time} \\
  \midrule
  Basic    & 2 Seconds \\
  Medium   & 2 Seconds \\
  Advanced & 3 Seconds \\
  \bottomrule
\end{tabular}
\end{center}

More powerful weapons generally reload more slowly, balancing their higher damage
and additional projectiles.

\subsection{Shooting and Damage System}

The Shooting and Damage System manages all combat interactions between the player
and enemies. It is responsible for processing mouse input, determining target
locations, spawning projectiles, simulating projectile trajectories, calculating
damage, and updating enemy health.

This subsystem represents the primary gameplay interaction mechanism and directly
affects player success and game progression.

\subsubsection{FR-15 Target Selection}

\paragraph{Purpose}
Allow players to select a target location within the battlefield.

\paragraph{Trigger}
The player presses the left mouse button.

\paragraph{Preconditions}
\begin{itemize}
  \item The game state is Playing.
  \item The click position is located inside the playable battlefield.
\end{itemize}

\paragraph{Main Flow}
\begin{enumerate}
  \item The player clicks a location on the battlefield.
  \item The system performs a raycast from the camera through the mouse position.
  \item The system determines the world-space intersection point.
  \item The system validates that the intersection point is located inside the
        battlefield.
  \item The system stores the target position.
  \item The system displays a visual target marker (``X'') at the selected
        position.
  \item The system immediately triggers a shooting action.
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-50: Only locations inside the battlefield shall be considered valid
        targets.
  \item BR-51: Invalid clicks shall be ignored.
  \item BR-52: A target marker shall appear immediately after a valid click.
  \item BR-53: The target marker shall indicate the intended projectile landing
        position.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Valid clicks generate a target marker.
  \item Invalid clicks do not generate a target marker.
  \item The marker appears at the selected position.
\end{itemize}

\subsubsection{FR-16 Projectile Creation}

\paragraph{Purpose}
Create projectiles when the player performs a shooting action.

\paragraph{Trigger}
A valid target location is selected.

\paragraph{Main Flow}
\begin{enumerate}
  \item The system identifies the currently equipped weapon.
  \item The system determines projectile properties.
  \item The system creates one or more projectile entities.
  \item The system assigns a launch position.
  \item The system assigns a target position.
  \item The projectile enters the Moving state.
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-54: The projectile shall be spawned immediately after a valid click.
  \item BR-55: The projectile origin shall be the weapon position.
  \item BR-56: The projectile target shall be the selected target position.
  \item BR-57: Advanced Weapon attacks shall spawn two projectiles.
  \item BR-133: A shooting action shall be ignored while the equipped weapon is
        reloading; no projectile or target marker shall be created until the
        reload completes (BR-130..132).
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Projectiles are created successfully.
  \item Projectile quantity matches weapon specifications.
\end{itemize}

\subsubsection{FR-17 Projectile Movement}

\paragraph{Purpose}
Simulate projectile travel from the weapon to the target location.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-58: Projectiles shall follow an arcing trajectory.
  \item BR-59: Projectiles shall not move in a straight line.
  \item BR-60: The projectile shall always land at the selected target position.
  \item BR-61: Projectile travel time depends on the equipped weapon.
\end{itemize}

\paragraph{Projectile Travel Speeds}
\begin{center}
\begin{tabular}{lc}
  \toprule
  \textbf{Weapon} & \textbf{Travel Speed} \\
  \midrule
  Basic    & Slow \\
  Medium   & Medium \\
  Advanced & Fast \\
  \bottomrule
\end{tabular}
\end{center}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Projectiles visibly travel through the air.
  \item Projectiles land at the selected target location.
  \item Faster weapons reach the target sooner.
\end{itemize}

\subsubsection{FR-18 Big Shot Mechanic}

\paragraph{Purpose}
Provide periodic high-damage attacks.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-62: Each weapon shall maintain an attack counter.
  \item BR-63: Only normal attacks contribute to the counter.
  \item BR-64: Reaching the required attack count shall prepare the next shot as
        a Big Shot.
\end{itemize}

\paragraph{Big Shot Requirements}
\begin{center}
\begin{tabular}{lcc}
  \toprule
  \textbf{Weapon} & \textbf{Trigger Count} & \textbf{Damage} \\
  \midrule
  Basic    & 3 Shots & 100 \\
  Medium   & 4 Shots & 120 \\
  Advanced & 5 Shots & 170 \\
  \bottomrule
\end{tabular}
\end{center}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Big Shots are generated at the correct intervals.
  \item Big Shots deal the correct amount of damage.
\end{itemize}

\subsubsection{FR-19 Damage Calculation}

\paragraph{Purpose}
Determine the amount of damage applied to enemies.

\paragraph{Trigger}
A projectile reaches its target position.

\paragraph{Main Flow}
\begin{enumerate}
  \item The projectile lands at the target position.
  \item The system calculates the distance between each enemy and the landing
        position.
  \item The system determines damage based on distance.
  \item The system reduces enemy health.
  \item The system checks whether the enemy has been destroyed.
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-65: Damage is calculated only when the projectile lands.
  \item BR-66: Damage is based on the enemy position at the moment of impact.
  \item BR-67: Enemies closer to the impact point receive more damage.
  \item BR-68: Enemies farther from the impact point receive less damage.
  \item BR-69: An enemy positioned exactly at the impact point receives full
        weapon damage.
\end{itemize}

\paragraph{Damage Formula}
Let:
\[ \text{Distance} = d \qquad \text{MaxRadius} = R \qquad \text{WeaponDamage} = D \]

Damage shall be calculated as:
\[ \text{Damage} = D \times \left(1 - \frac{d}{R}\right) \quad \text{for} \quad 0 \le d \le R \]

If $d > R$ then:
\[ \text{Damage} = 0 \]

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Enemies at the center of impact receive full damage.
  \item Damage decreases as distance increases.
  \item Enemies outside the damage radius receive no damage.
\end{itemize}

\subsubsection{FR-20 Enemy Destruction}

\paragraph{Purpose}
Remove enemies that have been defeated.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-70: Enemy health shall never be less than zero.
  \item BR-71: An enemy shall enter the Destroyed state when health reaches zero.
  \item BR-72: Destroyed enemies shall be removed from the active enemy list.
  \item BR-73: Destroyed enemies shall no longer participate in movement or
        collision processing.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Defeated enemies are removed from gameplay.
  \item Destroyed enemies no longer receive updates.
\end{itemize}

\subsection{Wave Progression System}

The Wave Progression System manages enemy composition, enemy spawning schedules,
weapon progression, and transitions between waves.

The game consists of three waves. Each wave contains a predefined number of
enemies with increasing difficulty. A wave is considered completed when all
enemies belonging to that wave have been destroyed.

\subsubsection{FR-21 Wave Configuration}

\paragraph{Purpose}
Define the composition of each gameplay wave.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-74: The game shall contain exactly three waves.
  \item BR-75: Wave 1 shall contain two Easy enemies and one Medium enemy.
  \item BR-76: Wave 2 shall contain two Easy enemies, two Medium enemies, and one
        Hard enemy.
  \item BR-77: Wave 3 shall contain two Easy enemies, two Medium enemies, and
        three Hard enemies.
  \item BR-78: Enemy quantities shall remain fixed throughout all game sessions.
\end{itemize}

\paragraph{Wave Composition}
\begin{center}
\begin{tabular}{ccccc}
  \toprule
  \textbf{Wave} & \textbf{Easy} & \textbf{Medium} & \textbf{Hard} & \textbf{Total} \\
  \midrule
  1 & 2 & 1 & 0 & 3 \\
  2 & 2 & 2 & 1 & 5 \\
  3 & 2 & 2 & 3 & 7 \\
  \bottomrule
\end{tabular}
\end{center}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Each wave contains the correct enemy composition.
  \item Enemy quantities match the predefined configuration.
\end{itemize}

\subsubsection{FR-22 Enemy Spawn Scheduling}

\paragraph{Purpose}
Control the timing of enemy creation.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-79: Easy enemies shall spawn every 3 seconds.
  \item BR-80: Medium enemies shall spawn every 4 seconds.
  \item BR-81: Hard enemies shall spawn every 5 seconds.
  \item BR-82: Enemies shall spawn sequentially.
  \item BR-83: A spawned enemy shall immediately enter the Move state.
  \item BR-84: Enemy spawning shall stop when all enemies belonging to the
        current wave have been created.
\end{itemize}

\paragraph{Spawn Timing}
\begin{center}
\begin{tabular}{lc}
  \toprule
  \textbf{Enemy Type} & \textbf{Spawn Interval} \\
  \midrule
  Easy   & 3 Seconds \\
  Medium & 4 Seconds \\
  Hard   & 5 Seconds \\
  \bottomrule
\end{tabular}
\end{center}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Enemies appear according to the specified schedule.
  \item No enemy spawns before its designated interval.
\end{itemize}

\subsubsection{FR-23 Wave Completion}

\paragraph{Purpose}
Determine when a wave has been successfully completed.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-85: A wave shall be completed when all enemies assigned to the wave
        have been destroyed.
  \item BR-86: A wave shall not complete while at least one enemy remains alive.
  \item BR-87: Enemy spawn schedules shall stop immediately after wave completion.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item The system correctly detects wave completion.
  \item Wave completion occurs only after all enemies are eliminated.
\end{itemize}

\subsubsection{FR-24 Wave Transition}

\paragraph{Purpose}
Transition from the current wave to the next wave.

\paragraph{Main Flow}
\begin{enumerate}
  \item The current wave is completed.
  \item The system displays a wave transition message.
  \item The transition message remains visible for 3 seconds.
  \item The next wave configuration is loaded.
  \item Enemy spawning begins for the next wave.
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-88: The message shall display the upcoming wave number.
  \item BR-89: The message shall remain visible for exactly 3 seconds.
  \item BR-90: Enemy spawning shall not occur while the transition message is
        displayed.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item The transition message appears after every completed wave.
  \item The next wave begins after the required delay.
\end{itemize}

\subsubsection{FR-25 Weapon Progression}

\paragraph{Purpose}
Reward players with stronger weapons as they progress.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-91: The player shall start the game with the Basic Weapon.
  \item BR-92: The Medium Weapon shall be unlocked after completing Wave 1.
  \item BR-93: The Advanced Weapon shall be unlocked after completing Wave 2.
  \item BR-94: Newly unlocked weapons shall automatically become active.
  \item BR-95: Weapon progression shall reset when a new game starts.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Weapon upgrades occur at the correct wave boundaries.
  \item The active weapon matches the current progression level.
\end{itemize}

\subsection{Runtime Control System}

The Runtime Control System allows players to manage the execution state of an
active gameplay session without leaving the game environment.

The subsystem provides controls for pausing, resuming, and restarting the game
while maintaining consistent synchronization between the user interface and the
application state.

\subsubsection{FR-26 Pause Functionality}

\paragraph{Purpose}
Temporarily suspend gameplay while preserving the current game state.

\paragraph{Trigger}
The player presses the Pause button.

\paragraph{Preconditions}
\begin{itemize}
  \item The game state is Playing.
\end{itemize}

\paragraph{Main Flow}
\begin{enumerate}
  \item The player presses Pause.
  \item The system changes the game state to Paused.
  \item Enemy movement is suspended.
  \item Enemy spawning is suspended.
  \item Projectile movement is suspended.
  \item Gameplay timers are suspended.
  \item The Pause overlay is displayed.
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-96: No gameplay updates shall occur while the game is paused.
  \item BR-97: The current game state shall be preserved.
  \item BR-98: User interface elements shall remain visible.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Enemy movement stops immediately.
  \item Projectiles stop immediately.
  \item Gameplay timers stop updating.
\end{itemize}

\subsubsection{FR-27 Resume Functionality}

\paragraph{Purpose}
Continue gameplay from a paused state.

\paragraph{Trigger}
The player presses the Resume button.

\paragraph{Preconditions}
\begin{itemize}
  \item The game state is Paused.
\end{itemize}

\paragraph{Main Flow}
\begin{enumerate}
  \item The player presses Resume.
  \item The system changes the game state to Playing.
  \item Enemy movement resumes.
  \item Enemy spawning resumes.
  \item Projectile movement resumes.
  \item Gameplay timers resume.
  \item The Pause overlay is removed.
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-99: Gameplay shall continue from the exact state prior to pausing.
  \item BR-100: No game data shall be reset during resume.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Gameplay continues from the previous state.
  \item Enemy and projectile movement resume correctly.
\end{itemize}

\subsubsection{FR-28 Restart Functionality}

\paragraph{Purpose}
Start a completely new gameplay session.

\paragraph{Trigger}
The player presses the Restart button.

\paragraph{Main Flow}
\begin{enumerate}
  \item The player presses Restart.
  \item The current session is terminated.
  \item All active enemies are removed.
  \item All active projectiles are removed.
  \item Wave progression is reset.
  \item Weapon progression is reset.
  \item The gameplay timer is reset.
  \item A new game session is initialized.
  \item The countdown sequence begins.
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-101: Restart shall always begin at Wave 1.
  \item BR-102: Restart shall always equip the Basic Weapon.
  \item BR-103: No gameplay data shall persist between sessions.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item A completely new game session begins.
  \item Previous session data is removed.
\end{itemize}

\subsection{Victory and Defeat System}

The Victory and Defeat System determines the outcome of a gameplay session and
presents the appropriate end-game interface to the player.

\subsubsection{FR-29 Defeat Condition}

\paragraph{Purpose}
Detect when the player fails to defend the house.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-104: A defeat shall occur when any enemy crosses the battlefield
        boundary protecting the house.
  \item BR-105: Defeat shall be triggered immediately upon boundary violation.
  \item BR-106: Enemy health and remaining enemies shall not affect defeat
        evaluation.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item The game immediately ends when an enemy reaches the protected area.
  \item The game state changes to Lose.
\end{itemize}

\subsubsection{FR-30 Defeat Screen}

\paragraph{Purpose}
Inform the player that the game has been lost.

\paragraph{Main Flow}
\begin{enumerate}
  \item A defeat condition is detected.
  \item The game state changes to Lose.
  \item All gameplay updates stop.
  \item A Lose overlay is displayed.
  \item A Restart button is displayed.
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-107: Enemy spawning shall stop.
  \item BR-108: Enemy movement shall stop.
  \item BR-109: Projectile updates shall stop.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item The Lose overlay is displayed.
  \item The Restart button is available.
\end{itemize}

\subsubsection{FR-31 Victory Condition}

\paragraph{Purpose}
Detect successful completion of the game.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-110: Victory shall occur after Wave 3 has been completed.
  \item BR-111: All enemies belonging to Wave 3 shall be destroyed.
  \item BR-112: No active enemies may remain in the game world.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Victory is triggered only after all Wave 3 enemies are defeated.
  \item The game state changes to Win.
\end{itemize}

\subsubsection{FR-32 Victory Screen}

\paragraph{Purpose}
Inform the player that the game has been successfully completed.

\paragraph{Main Flow}
\begin{enumerate}
  \item The victory condition is detected.
  \item The game state changes to Win.
  \item Gameplay updates stop.
  \item A Victory overlay is displayed.
  \item A Return to Start Page button is displayed.
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-113: Enemy spawning shall stop.
  \item BR-114: Enemy movement shall stop.
  \item BR-115: Projectile updates shall stop.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item The Victory overlay is displayed.
  \item The Return to Start Page button is available.
\end{itemize}

\subsubsection{FR-33 Return to Start Page}

\paragraph{Purpose}
Allow players to return to the Welcome Screen after winning.

\paragraph{Trigger}
The player presses the Return to Start Page button.

\paragraph{Main Flow}
\begin{enumerate}
  \item The player presses Return to Start Page.
  \item The current session is terminated.
  \item All gameplay data is cleared.
  \item The Welcome Screen is displayed.
\end{enumerate}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item The Welcome Screen is displayed.
  \item A new session can be started.
\end{itemize}

\subsection{Heads-Up Display (HUD)}

The Heads-Up Display (HUD) provides real-time gameplay information and controls
without interrupting gameplay.

The HUD shall remain visible throughout active gameplay and shall continuously
synchronize with the current game state.

\subsubsection{FR-30 Wave Information Display}

\paragraph{Purpose}
Display the current progression of the game.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-96: The current wave number shall be displayed.
  \item BR-97: The displayed wave shall update immediately after a wave
        transition.
  \item BR-98: The wave indicator shall remain visible during gameplay.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item The correct wave number is displayed.
  \item Wave updates are reflected immediately.
\end{itemize}

\subsubsection{FR-31 Gameplay Timer}

\paragraph{Purpose}
Display the elapsed gameplay time.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-99: The timer shall start when gameplay enters the Playing state.
  \item BR-100: The timer shall update every second.
  \item BR-101: The timer shall pause when the game is paused.
  \item BR-102: The timer shall stop when the game ends.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item The timer increases correctly.
  \item The timer pauses and resumes correctly.
\end{itemize}

\subsection{Rendering System}

The Rendering System is responsible for displaying all visual elements of the
game world using Three.js and WebGL.

The subsystem converts application state into a visual representation that can be
observed and interacted with by the player.

\subsubsection{FR-32 Scene Rendering}

\paragraph{Purpose}
Render the complete gameplay environment.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-103: The battlefield shall be rendered continuously.
  \item BR-104: The house shall be rendered throughout gameplay.
  \item BR-105: Enemy entities shall be rendered while active.
  \item BR-106: Projectiles shall be rendered while active.
  \item BR-107: Destroyed entities shall no longer be rendered.
\end{itemize}

\subsubsection{FR-33 Camera Management}

\paragraph{Purpose}
Provide a consistent view of the battlefield.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-108: The application shall use a perspective camera.
  \item BR-109: The entire battlefield shall remain visible.
  \item BR-110: Camera positioning shall support accurate target selection.
\end{itemize}

\subsubsection{FR-34 Lighting System}

\paragraph{Purpose}
Provide visual clarity and depth perception.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-111: Ambient lighting shall illuminate the scene.
  \item BR-112: Directional lighting shall simulate sunlight.
  \item BR-113: Major scene objects shall support shadow rendering.
\end{itemize}

\subsubsection{FR-35 Animation Rendering}

\paragraph{Purpose}
Display visual motion of entities.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-114: Enemy movement shall be animated.
  \item BR-115: Projectile movement shall be animated.
  \item BR-116: Target markers shall be rendered immediately after selection.
  \item BR-117: Animations shall update every render frame.
\end{itemize}

\subsubsection{FR-40 Damage Hit Feedback}

\paragraph{Purpose}
Give the player clear visual confirmation that a projectile damaged an enemy.

\paragraph{Trigger}
An enemy's health is reduced by a projectile impact.

\paragraph{Main Flow}
\begin{enumerate}
  \item A projectile lands and applies area-of-effect damage.
  \item Each enemy that loses health briefly flashes a red glow.
  \item The glow fades out over a short duration.
  \item The enemy resumes its normal appearance.
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-134: An enemy that receives damage shall display a red glow (hit flash).
  \item BR-135: The hit flash shall be brief and fade out automatically.
  \item BR-136: Enemies that receive no damage shall not flash.
  \item BR-137: The hit flash shall be purely visual and shall not affect enemy
        health, movement, or collision.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Damaged enemies visibly flash red on impact.
  \item The flash fades shortly after the hit.
  \item Enemies outside the blast radius do not flash.
\end{itemize}

\subsection{Physics and Collision System}

The Physics and Collision System manages projectile movement, impact detection,
and spatial calculations required by gameplay mechanics.

\subsubsection{FR-36 Projectile Physics}

\paragraph{Purpose}
Simulate projectile travel through the battlefield.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-118: Projectiles shall follow a ballistic trajectory.
  \item BR-119: Projectile travel time shall depend on the equipped weapon.
  \item BR-120: Projectiles shall land exactly at the selected target position.
\end{itemize}

\subsubsection{FR-37 Impact Detection}

\paragraph{Purpose}
Detect projectile arrival at the target position.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-121: An impact event shall occur when a projectile reaches its target
        position.
  \item BR-122: Impact processing shall execute only once per projectile.
  \item BR-123: The projectile shall enter the Remove state after impact.
\end{itemize}

\subsubsection{FR-38 Area-of-Effect Collision}

\paragraph{Purpose}
Determine which enemies are affected by an impact.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-124: The system shall calculate the distance between the impact point
        and every active enemy.
  \item BR-125: Enemies within the effect radius shall receive damage.
  \item BR-126: Enemies outside the effect radius shall receive no damage.
\end{itemize}

\subsubsection{FR-39 Entity Cleanup}

\paragraph{Purpose}
Remove inactive entities from the game world.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-127: Destroyed enemies shall be removed.
  \item BR-128: Expired projectiles shall be removed.
  \item BR-129: Removed entities shall no longer participate in updates or
        rendering.
\end{itemize}

\subsection{Leaderboard and Ranking System}

The Leaderboard and Ranking System records completed runs and ranks players
against one another. It spans the client (name capture, result display) and a
lightweight server-side service that persists scores and returns them in ranked
order.

A run is described by the player's name, the total time taken, the furthest wave
reached, and whether all three waves were cleared. The ranking favours players
who clear the game fastest, while still placing players who progressed further
above those who did not.

\subsubsection{FR-42 Player Name Entry}

\paragraph{Purpose}
Capture an optional display name so a run can be attributed to the player on the
leaderboard.

\paragraph{Main Flow}
\begin{enumerate}
  \item The Welcome Screen presents a name input and two ways to start: ``Play
        with Name'' and ``Pass''.
  \item The player either enters a name and starts a recorded session, or chooses
        ``Pass'' to play anonymously.
  \item The chosen name is retained for the session.
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-144: The Welcome Screen shall provide a field for entering a player
        name.
  \item BR-145: ``Play with Name'' shall start a session whose result is recorded
        under the entered name.
  \item BR-146: ``Pass'' shall start an anonymous session that is not recorded.
  \item BR-147: The entered name shall be retained across Restart so a retry is
        still recorded, and shall be cleared on return to the Welcome Screen.
  \item BR-148: The name shall be trimmed and limited to a maximum of 20
        characters.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item A named session starts only when a non-empty name is entered.
  \item An anonymous session can always be started with ``Pass''.
\end{itemize}

\subsubsection{FR-43 Run Recording}

\paragraph{Purpose}
Persist the outcome of a finished run so it can appear on the leaderboard.

\paragraph{Trigger}
The game reaches the Win or Lose state during a named session.

\paragraph{Main Flow}
\begin{enumerate}
  \item The system determines the total play time, the furthest wave reached, and
        whether the game was won.
  \item The system submits the run to the leaderboard service through the HTTP
        API.
  \item The service validates and stores the run.
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-149: A run shall be recorded exactly once, at game end (win or lose).
  \item BR-150: Anonymous (Pass) runs shall not be recorded.
  \item BR-151: The recorded time shall be the total active play time of the
        session.
  \item BR-152: The recorded wave shall be the furthest wave reached, and the win
        flag shall be true only when all three waves are cleared.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Finishing a named game adds exactly one entry to the leaderboard.
  \item Anonymous games add no entry.
\end{itemize}

\subsubsection{FR-44 Ranking Rules}

\paragraph{Purpose}
Define a single, consistent order for all recorded runs.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-153: Players who clear all three waves shall rank above players who do
        not.
  \item BR-154: Among players who cleared the game, a shorter completion time
        shall rank higher.
  \item BR-155: Among players who did not clear the game, runs shall be grouped by
        furthest wave reached, with higher waves ranking above lower waves.
  \item BR-156: Players who did not clear the game shall not be ranked by time;
        within the same wave, more recent runs shall appear first.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Winners appear first, ordered by fastest time.
  \item Non-winners follow, grouped from the deepest wave to the shallowest.
\end{itemize}

\subsubsection{FR-45 Leaderboard Display}

\paragraph{Purpose}
Show the ranked standings to the player.

\paragraph{Main Flow}
\begin{enumerate}
  \item The system requests the ranked leaderboard from the service.
  \item The system displays, for each entry, its rank, name, result (cleared or
        wave reached), and time.
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-157: The leaderboard shall display rank, name, result, and time for
        each entry.
  \item BR-158: The leaderboard shall be viewable from the Welcome Screen and
        shall be shown on the Win and Lose screens.
  \item BR-159: When shown after a game, the player's most recent run shall be
        highlighted.
  \item BR-160: The leaderboard shall present clear loading, empty, and error
        states.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item The board reflects the ranking rules (FR-44).
  \item The player's newly recorded run is highlighted on the end screen.
\end{itemize}

\subsubsection{FR-46 Leaderboard Service}

\paragraph{Purpose}
Provide persistent storage and a defined interface for leaderboard data.

\paragraph{Business Rules}
\begin{itemize}
  \item BR-161: Scores shall be stored in a persistent server-side data store.
  \item BR-162: The client shall access the store only through the HTTP API: one
        operation to record a run and one to retrieve the ranked list.
  \item BR-163: The service shall validate submitted runs and reject malformed
        data.
  \item BR-164: Retrieval shall return entries already ordered by the ranking
        rules (FR-44).
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Valid runs are stored and retrievable; malformed submissions are rejected.
  \item The retrieved list is already in ranked order.
\end{itemize}

\subsection{Enemy Health Indicator}

\subsubsection{FR-41 Enemy Health Bar}

\paragraph{Purpose}
Show each enemy's remaining health directly above it, so the player can gauge how
close a monster is to being destroyed and prioritize targets.

\paragraph{Main Flow}
\begin{enumerate}
  \item When an enemy appears, a health bar is displayed above it.
  \item The bar always faces the camera.
  \item The filled portion reflects the enemy's current health as a fraction of
        its maximum health.
  \item The fill color transitions from green through yellow to red as the enemy
        loses health.
  \item The bar follows the enemy as it moves and is removed when the enemy is
        destroyed.
\end{enumerate}

\paragraph{Business Rules}
\begin{itemize}
  \item BR-138: A health bar shall be displayed above every enemy from the moment
        it spawns.
  \item BR-139: The filled length of the bar shall be proportional to the enemy's
        current health divided by its maximum health.
  \item BR-140: The fill color shall transition from green (full health) through
        yellow to red (low health).
  \item BR-141: The health bar shall always face the camera.
  \item BR-142: The health bar shall follow the enemy and shall be removed when
        the enemy is destroyed.
  \item BR-143: The health bar shall be purely visual and shall not affect enemy
        health, movement, or collision.
\end{itemize}

\paragraph{Acceptance Criteria}
\begin{itemize}
  \item Every enemy displays a health bar as soon as it spawns.
  \item The bar shrinks and changes color as the enemy loses health.
  \item The bar disappears when the enemy is destroyed.
\end{itemize}

% ===========================================================================
\section{Non-Functional Requirements}

\subsection{Performance Requirements}

The application shall maintain an average frame rate of at least 30 FPS under
normal gameplay conditions on a modern desktop browser.

The system shall render user interactions, animations, and scene updates with
minimal perceptible delay.

The loading time for the initial game scene should not exceed 10 seconds under
normal network conditions.

The application shall efficiently manage 3D assets and memory usage to prevent
significant performance degradation during gameplay.

The system shall support real-time updates of game entities, animations, and
visual effects without causing noticeable interruptions to the user experience.

\subsection{Usability Requirements}

The application shall provide an intuitive user interface that allows users to
understand the gameplay mechanics without extensive instructions.

User interactions shall be performed using standard mouse controls commonly
available on desktop devices.

The visual feedback generated by the system shall clearly indicate successful
actions, collisions, and game state transitions.

The interface shall present relevant gameplay information through HUD elements and
overlay screens when necessary.

The system shall provide clear indications of victory, defeat, and game
progression.

\subsection{Reliability Requirements}

The application shall maintain stable operation throughout a complete gameplay
session.

Unexpected user inputs shall not cause application crashes or unresponsive states.

The system shall correctly manage game state transitions between initialization,
active gameplay, pause, victory, and defeat states.

The application shall ensure that game entities are properly created, updated, and
removed during runtime.

The system shall recover gracefully from asset loading failures whenever possible.

\subsection{Compatibility Requirements}

The application shall support modern desktop web browsers that provide WebGL
support.

The system shall be compatible with recent versions of Google Chrome, Microsoft
Edge, Mozilla Firefox, and other Chromium-based browsers.

The application shall operate without requiring users to install additional
software or plugins.

The system shall be deployable as a standard web application using the Next.js
framework.

\subsection{Maintainability Requirements}

The source code shall follow a modular architecture to facilitate future
development and maintenance activities.

Application logic, rendering logic, user interface components, and state
management mechanisms shall be separated into independent modules whenever
possible.

The project shall utilize TypeScript to improve code reliability, readability, and
maintainability through static type checking.

Reusable components and utility functions shall be organized to minimize code
duplication.

The codebase shall support future feature additions with minimal impact on
existing functionality.

% ===========================================================================
\section{Future Enhancements}

Although the current implementation focuses on the core gameplay and frontend
architecture defined in the project proposal, the system has been designed with
extensibility in mind. Several enhancements may be considered in future
development phases.

\subsection{Ranking Enhancements}

The existing leaderboard (Leaderboard and Ranking System) may be extended to
compare player performance in richer ways.

Additional metrics such as accuracy, enemies defeated, and per-weapon statistics
could be recorded alongside the existing time and wave data, and presented
through expanded leaderboard views and filters.

\subsection{Backend Integration}

The existing leaderboard service may be expanded into a fuller backend to support
online functionality beyond a single device.

Potential features include player accounts, game progress tracking, statistics
collection, cloud-based configuration management, and cross-device
synchronization of leaderboard records.

The expansion could migrate the current local store to a hosted database while
preserving the existing HTTP API and frontend architecture.

\subsection{Additional Monster Types}

Future versions of the application may introduce new monster types with distinct
visual appearances, movement patterns, health values, and attack behaviors.

Additional enemy variations could increase gameplay diversity and provide more
complex interaction scenarios for the player.

\subsection{Additional Weapons}

The weapon system may be extended to support a larger variety of weapons, each
with unique projectile properties, firing rates, damage values, and visual
effects.

Examples include explosive projectiles, rapid-fire weapons, area-of-effect
attacks, and specialized defensive weapons.

\end{document}
